\documentclass{article}

% Language setting
% Replace `english' with e.g. `spanish' to change the document language
\usepackage[english]{babel}
\usepackage{enumerate}

% Set page size and margins
% Replace `letterpaper' with `a4paper' for UK/EU standard size
\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{titling}

\usepackage{listings}
\usepackage{xcolor}

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}

\lstset{style=mystyle}

\setlength{\parskip}{\baselineskip}%
\setlength{\parindent}{0pt}%


\begin{document}

\title{Embedded System User Manual}
\date{} 
\author{Elina Rosato \and Danielis Maizelis}

% title page
\maketitle

%\begin{abstract}
%Your abstract.
%\end{abstract}

% table of contents
\tableofcontents
\newpage

% section 1: introduction
\section{Introduction}

This section should provide an overview of the purpose of the manual and the embedded system it covers.

% section 2: system overview
\section{System Overview}

This section should provide an overview of the embedded system, including its architecture, components, and interfaces.

% section 3: hardware requirements
\section{Hardware Requirements}

This section should list the hardware requirements for the embedded system, including any specific components that are necessary for proper operation.

% section 4: software requirements
\section{Software Requirements}

This section should list the software requirements for the embedded system, including any specific operating systems, drivers, or applications that are necessary for proper operation.

% section 5: installation
\section{Installation}

This section should provide step-by-step instructions for installing the embedded system, including any necessary software and hardware.

% section 6: usage
\section{Usage}

This section should provide instructions for using the embedded system, including how to interact with the system and any specific features or capabilities.

% section 7: troubleshooting
\section{Troubleshooting}

This section should provide guidance for troubleshooting common issues that may arise when using the embedded system.

% section 8: support and contact information
\section{Support and Contact Information}

This section should provide contact information for obtaining support or additional assistance with the embedded system.

% appendix
\appendix
\section{Appendix}

This section can include additional information that may be helpful to users, such as technical specifications, diagrams, or reference material.

% references
\begin{thebibliography}{9}
\bibitem{example}
    Author,
    \emph{Title},
    Publisher, Year.
\end{thebibliography}


\end{document}